Manuscript

### 2016-03-06 inst/simulation/manuscript.Rmd
...

```{r figure-3sample}
#xlim <- log10(c(30,800)); ylim <- xlim
logPopulationSizesSample <- subset(logPopulationSizes, scenario == "A")
logPopulationSizesSample <- cutoffPopulationSizes(logPopulationSizesSample, cutoff, models=modelNames[c(1,3,5)])
logPopulationSizesSample$modelName <- prettyModelName(logPopulationSizesSample$modelName)
logPopulationSizesSample <- rbind(
  subset(logPopulationSizesSample, modelName=="ST"),
  subset(logPopulationSizesSample, modelName=="T1"),
  subset(logPopulationSizesSample, modelName=="T2"),
  subset(logPopulationSizesSample, modelName=="FMP"))

@@

  p <- ggplot(size, aes(Observed, Estimated, colour=modelName)) +
    geom_point(size=1, colour="darkgray", alpha=.5) +
    geom_abline(colour="black", linetype="longdash") + 
    geom_point(data=meanSize, aes(True, Estimated), size=2, shape=15, colour="black")

@@

  p <- p + facet_wrap(~modelName) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(10^.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(10^.x))) +
    xlab("True population size") + ylab("Estimated population size") +
    theme_ms() + theme(panel.border=element_rect(fill="transparent"),
                                        plot.title=element_text(size=10),
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))

@@

p <- plotLogPopulationSizeSample(subset(logPopulationSizesSample, modelName %in% c("ST","T1","T2","FMP")), modelName=c("ST","T1","T2","FMP"), "a", xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3sample.png", height=7.87, width=17) # draft quality
saveFigure(p, "manuscript-figure-3sample.pdf", height=7.87, width=17, dpi=300)
```

@@

  p <- p + facet_wrap(~Scenario) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(.x))) +
    xlab(expression(paste(Log[10], " true population size"))) + ylab(expression(paste(Log[10], " estimated population size"))) + ggtitle(paste("Model:", prettyModelName(modelName[1]))) +
    theme_ms() + theme(panel.border=element_rect(fill="transparent"),
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))

>>>>

```{r figure-3sample}
logPopulationSizesSample <- subset(logPopulationSizes, scenario == "A")
logPopulationSizesSample <- cutoffPopulationSizes(logPopulationSizesSample, cutoff, models=modelNames[c(1,3,5)])
logPopulationSizesSample$modelName <- prettyModelName(logPopulationSizesSample$modelName)
logPopulationSizesSample <- rbind(
  subset(logPopulationSizesSample, modelName=="ST"),
  subset(logPopulationSizesSample, modelName=="T1"),
  subset(logPopulationSizesSample, modelName=="T2"),
  subset(logPopulationSizesSample, modelName=="FMP"))

@@

  p <- ggplot(size, aes(Observed, Estimated, colour=modelName)) +
    geom_point(size=1, colour="gray40", alpha=.5) +
    geom_abline(colour="black", linetype="longdash") + 
    geom_point(data=meanSize, aes(True, Estimated), size=2, shape=15, colour="black")

@@

  p <- p + facet_wrap(~modelName) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(10^.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(10^.x))) +
    xlab("True population size") + ylab("Estimated population size") +
    theme_ms2() + theme(panel.border=element_rect(fill="transparent"),
                                        plot.title=element_text(size=10),
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))

@@

p <- plotLogPopulationSizeSample(subset(logPopulationSizesSample, modelName %in% c("ST","T1","T2","FMP")), modelName=c("ST","T1","T2","FMP"), "a", xlim=log10(c(1, 10^3)), ylim=log10(c(1,10^3)))
saveFigure(p, "manuscript-figure-3sample.png", height=7.87, width=17) # draft quality
saveFigure(p, "manuscript-figure-3sample.pdf", height=7.87, width=17, dpi=300)
```

@@

  p <- p + facet_wrap(~Scenario) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(.x))) +
    xlab(expression(paste(Log[10], " true population size"))) + ylab(expression(paste(Log[10], " estimated population size"))) + ggtitle(paste("Model:", prettyModelName(modelName[1]))) +
    theme_ms2() + theme(panel.border=element_rect(fill="transparent"),
                                        legend.margin=unit(0, units="line"),
                                        panel.margin=unit(0, units="line"))
